Supporting Information : The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2019-02-05 SupportingInformation.Rmd
fixed typo
edits of Q2 methods and results

\begin{figure}[!h]
\begin{center}
\includegraphics[width=6 cm,height=6 cm]{./stat_image.jpg} \hspace{0.6 cm}
\caption[For definitions of nonparametric statistics]{Schematic diagram supporting definitions of nonparametric tail dependence statistics. The red and blue lines are, respectively, $u+v=2l_b$ and $u+v=2u_b$.\label{fig_stat_image}}
\end{center}
\end{figure}

@@

# Surrogate testing with bivariate datasets for non-parametric statistics \label{surrog_test}

For bivariate datasets, surrogates were produced as follows.

- Given data $(x_i,y_i)$ for $i=1,\ldots,n$ and a 
one-parameter target copula family $\mathcal{B}(\theta)$ (here $\theta$ denotes the parameter), let $\tau$ be the
Kendall correlation of the $x_i$ with the $y_i$ and find the parameter value $\theta_\tau$ for which 
$\mathcal{B}(\theta_\tau)$ has Kendall correlation $\tau$ (this is possible for the one-parameter copula families of this 
study using the `iTau` function of the `VineCopula` package). 
- Generate data $(a_i,b_i)$, $i=1,\ldots,n$ from 
$\mathcal{B}(\theta_\tau)$. 
- Permute the ordered set $(x_1,\ldots,x_n)$ such that the permutation
$(x_{\sigma_x(1)},\ldots,x_{\sigma_x(n)})$ has $\rank(x_{\sigma_x(i)})$ equal to $\rank(a_i)$ for all $i$, where 
$\rank(x_{\sigma_x(i)})$ is the rank of $x_{\sigma_x(i)}$ in the set $(x_{\sigma_x(1)},\ldots,x_{\sigma_x(n)})$, and
$\rank(a_i)$ is the rank of $a_i$ in the set $(a_1,\ldots,a_n)$ (here $\sigma_x$ is a permutation of the 
indices $1,\ldots,n$). 
- Likewise permute $(y_1,\ldots,y_n)$
such that the permutation
$(y_{\sigma_y(1)},\ldots,y_{\sigma_y(n)})$ has $\rank(y_{\sigma_y(i)})$ equal to $\rank(b_i)$ for all $i$ ($\sigma_y$ is 
another permutation of $1,\ldots,n$).
- The surrogate dataset is $(x_{\sigma_x(i)},y_{\sigma_y(i)})$ for $i=1,\ldots,n$.

\noindent Our code for this algorithm is `copsurrog2d` in the 
`BIVAN` repository (https://github.com/sghosh89/BIVAN). 
Because $(x_{\sigma_x(1)},\ldots,x_{\sigma_x(n)})$ 
is a permutation of $(x_1,\ldots,x_n)$ and $(y_{\sigma_y(1)},\ldots,y_{\sigma_y(n)})$ is a 
permutation 
of $(y_1,\ldots,y_n)$, the marginal distributions of the surrogate data are exactly the same as 
those of the original data. 
Because ranks of the surrogate data are matched to ranks of the $a_i$ and $b_i$, the
Kendall correlation of the surrogate dataset will be the same as that of the $a_i$ and $b_i$, and therefore 
will be close to $\tau$ (differences arising only through sampling variation). If instead of $\theta_\tau$
a parameter value $\theta_\rho$ is used such that the Spearman correlation of $\mathcal{B}(\theta_\rho)$ is the same
as that of the $x_i$ with the $y_i$, then Spearman correlations of surrogates will very nearly equal (except for 
sampling variation) the Spearman correlation of the empirical data.

@@

<!--Do the main computations for non-parametric analysis of aphid count data-->
```{r stat_aphid_count, echo=F, cache=T, cache.extra=list(seed,data_aphid_count,mtime("good_loclist.R"),mtime("NonParamStat.R"),mtime("vivj_matrix.R"),mtime("CopulaFunctions.R"), mtime("CopulaFunctions_flexible.R"))}

@@

<!--Do the main computations for non-parametric analysis of aphid ff data-->
```{r stat_aphid_ff, echo=F, cache=T,  cache.extra=list(seed,data_aphid_ff,mtime("good_loclist.R"),mtime("NonParamStat.R"),mtime("vivj_matrix.R"),mtime("CopulaFunctions.R"), mtime("CopulaFunctions_flexible.R"))}

@@

<!--
\newpage
## Results: abundance data for *Ceratium furca* in UK seas \label{Ex_pns}
### Model selection approach \label{Ex_pns_Model_selection}
### Non-parametric analysis of tail dependence  \label{Ex_pns_NPA}
                          ----moved to Paper.Rmd----
-->

@@

<!--Do the main computations for non-parametric analysis of plankton data-->
```{r stat_plankton_north_sea, echo=F, cache=T, cache=T,  cache.extra=list(seed,data_plankton_north_sea,longs_pns,lats_pns,mtime("good_loclist.R"),mtime("NonParamStat.R"),mtime("vivj_matrix.R"),mtime("CopulaFunctions.R"), mtime("CopulaFunctions_flexible.R"))}

@@

<!--Do the main computations for non-parametric analysis of methane-flux data-->
```{r stat_methane, echo=F, cache=T, cache=T,  cache.extra=list(seed,methane_data,mtime("good_loclist.R"),mtime("NonParamStat.R"),mtime("vivj_matrix.R"),mtime("CopulaFunctions.R"), mtime("CopulaFunctions_flexible.R"))}

@@

\begin{figure}[!h]
\begin{center}
\includegraphics[width=13 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Clayton/common_legend_cause4copula_stat.pdf}\\
\vspace{-0.4 cm}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Clayton/Clayton_Spearman_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Clayton/Clayton_Kendall_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Clayton/Clayton_Pearson_vs_Kendall's Tau.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Clayton/Clayton_Corl_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Clayton/Clayton_Coru_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Clayton/Clayton_Corl-Coru_vs_Kendall's Tau.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Clayton/Clayton_Pl_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Clayton/Clayton_Pu_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Clayton/Clayton_Pl-Pu_vs_Kendall's Tau.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Clayton/Clayton_D2u_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Clayton/Clayton_D2l_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Clayton/Clayton_D2u-D2l_vs_Kendall's Tau.pdf}
\caption[AR(1) model : comparing correlations and non-parametric statistic for between noise-copula (\textbf{Clayton}) and population copula for different Kendall's correlation]{AR(1) model : results of comparison between 3 types of correlation (i.e. Spearman, Kendall, Pearson) and 6 non-parametric stats ($\cor_l$, $\cor_u$, $\Ps_l$, $\Ps_u$, $\Dsq_u$ and $\Dsq_l$) of environmental noise generated from lower tail dependent \textbf{Clayton} copula and of the affected populations for 9 equidistant Kendall's correlation ($\tau$) values in a range (0.1 to 0.9) (Initially $5000$ points are generated but we kept last $500$ points for both noise and population data for comparison). p-values from paired t-test if $> 0.05$ (above horizontal purple line) indicates exactly same estimate between noise and population copulae. \label{fig_Cause4copula_C_kend_ar1}}
\end{center}
\end{figure}

\begin{figure}[!h]
\begin{center}
\includegraphics[width=13 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Survival Clayton/common_legend_cause4copula_stat.pdf}\\
\vspace{-0.4 cm}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Survival Clayton/Survival Clayton_Spearman_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Survival Clayton/Survival Clayton_Kendall_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Survival Clayton/Survival Clayton_Pearson_vs_Kendall's Tau.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Survival Clayton/Survival Clayton_Corl_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Survival Clayton/Survival Clayton_Coru_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Survival Clayton/Survival Clayton_Corl-Coru_vs_Kendall's Tau.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Survival Clayton/Survival Clayton_Pl_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Survival Clayton/Survival Clayton_Pu_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Survival Clayton/Survival Clayton_Pl-Pu_vs_Kendall's Tau.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Survival Clayton/Survival Clayton_D2u_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Survival Clayton/Survival Clayton_D2l_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Survival Clayton/Survival Clayton_D2u-D2l_vs_Kendall's Tau.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Survival Clayton/Survival Clayton_scatter_CorlmCoru_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Survival Clayton/Survival Clayton_scatter_PlmPu_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Survival Clayton/Survival Clayton_scatter_D2umD2l_Kendall's Tau.pdf}
\caption[AR(1) model : comparing correlations and non-parametric statistic between noise-copula (\textbf{Survival Clayton}) and population copula for different Kendall's correlation]{AR(1) model : results of comparison between 3 types of correlation (i.e. Spearman, Kendall, Pearson) and 6 non-parametric stats ($\cor_l$, $\cor_u$, $\Ps_l$, $\Ps_u$, $\Dsq_u$ and $\Dsq_l$) of environmental noise generated from upper tail dependent \textbf{Survival Clayton} copula and of the affected populations for 9 equidistant Kendall's correlation ($\tau$) values in a range (0.1 to 0.9) (Initially $5000$ points are generated but we kept last $500$ points for both noise and population data for comparison). p-values from paired t-test if $> 0.05$ (above horizontal purple line) indicates exactly same estimate between noise and population copulae. Last row in the figure compared the linear regression line with the 1:1 green line and if noise and population tail-dependence stats came up with pearson correlation p-value $< 0.05$, then they are significantly similar.\label{fig_Cause4copula_SC_kend_ar1}}
\end{center}
\end{figure}

\begin{figure}[!h]
\begin{center}
\includegraphics[width=13 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Gumbel/common_legend_cause4copula_stat.pdf}\\
\vspace{-0.4 cm}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Gumbel/Gumbel_Spearman_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Gumbel/Gumbel_Kendall_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Gumbel/Gumbel_Pearson_vs_Kendall's Tau.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Gumbel/Gumbel_Corl_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Gumbel/Gumbel_Coru_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Gumbel/Gumbel_Corl-Coru_vs_Kendall's Tau.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Gumbel/Gumbel_Pl_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Gumbel/Gumbel_Pu_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Gumbel/Gumbel_Pl-Pu_vs_Kendall's Tau.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Gumbel/Gumbel_D2u_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Gumbel/Gumbel_D2l_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Gumbel/Gumbel_D2u-D2l_vs_Kendall's Tau.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Gumbel/Gumbel_scatter_CorlmCoru_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Gumbel/Gumbel_scatter_PlmPu_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Gumbel/Gumbel_scatter_D2umD2l_Kendall's Tau.pdf}
\caption[AR(1) model : comparing correlations and non-parametric statistic between noise-copula (\textbf{Gumbel}) and population copula for different Kendall's correlation]{AR(1) model: similar analysis as depicted in Fig. \ref{fig_Cause4copula_SC_kend_ar1} but for noise generated from upper tail dependent \textbf{Gumbel} copula. \label{fig_Cause4copula_G_kend_ar1}}
\end{center}
\end{figure}

>>>>

\begin{figure}[!h]
\begin{center}
\includegraphics[width=6 cm,height=6 cm]{./stat_image.jpg} \hspace{0.6 cm}
\caption[For definitions of nonparametric statistics]{Schematic diagram supporting definitions of nonparametric tail dependence statistics. The blue and red lines are, respectively, $u+v=2l_b$ and $u+v=2u_b$.\label{fig_stat_image}}
\end{center}
\end{figure}

@@

# Surrogate testing with bivariate datasets for nonparametric statistics \label{surrog_test}

For bivariate data sets, surrogates were produced as follows.

- Given data $(x_i,y_i)$ for $i=1,\ldots,n$ and a 
one-parameter target copula family $\mathcal{B}(\theta)$ (here $\theta$ denotes the parameter), let $\tau$ be the
Kendall correlation of the $x_i$ with the $y_i$ and find the parameter value $\theta_\tau$ for which 
$\mathcal{B}(\theta_\tau)$ has Kendall correlation $\tau$ (this is possible for the one-parameter copula families of this 
study using the `iTau` function of the `VineCopula` package). 
- Generate data $(a_i,b_i)$, $i=1,\ldots,n$ from 
$\mathcal{B}(\theta_\tau)$. 
- Permute the ordered set $(x_1,\ldots,x_n)$ such that the permutation
$(x_{\sigma_x(1)},\ldots,x_{\sigma_x(n)})$ has $\rank(x_{\sigma_x(i)})$ equal to $\rank(a_i)$ for all $i$, where 
$\rank(x_{\sigma_x(i)})$ is the rank of $x_{\sigma_x(i)}$ in the set $(x_{\sigma_x(1)},\ldots,x_{\sigma_x(n)})$, and
$\rank(a_i)$ is the rank of $a_i$ in the set $(a_1,\ldots,a_n)$ (here $\sigma_x$ is a permutation of the 
indices $1,\ldots,n$). 
- Likewise permute $(y_1,\ldots,y_n)$
such that the permutation
$(y_{\sigma_y(1)},\ldots,y_{\sigma_y(n)})$ has $\rank(y_{\sigma_y(i)})$ equal to $\rank(b_i)$ for all $i$ ($\sigma_y$ is 
another permutation of $1,\ldots,n$).
- The surrogate data set is $(x_{\sigma_x(i)},y_{\sigma_y(i)})$ for $i=1,\ldots,n$.

\noindent Our code for this algorithm is `copsurrog2d` in the 
`BIVAN` repository (https://github.com/sghosh89/BIVAN). 
Because $(x_{\sigma_x(1)},\ldots,x_{\sigma_x(n)})$ 
is a permutation of $(x_1,\ldots,x_n)$ and $(y_{\sigma_y(1)},\ldots,y_{\sigma_y(n)})$ is a 
permutation 
of $(y_1,\ldots,y_n)$, the marginal distributions of the surrogate data are exactly the same as 
those of the original data. 
Because ranks of the surrogate data are matched to ranks of the $a_i$ and $b_i$, the
Kendall correlation of the surrogate data set will be the same as that of the $a_i$ and $b_i$, and therefore 
will be close to $\tau$ (differences arising only through sampling variation). If instead of $\theta_\tau$
a parameter value $\theta_\rho$ is used such that the Spearman correlation of $\mathcal{B}(\theta_\rho)$ is the same
as that of the $x_i$ with the $y_i$, then Spearman correlations of surrogates will very nearly equal (except for 
sampling variation) the Spearman correlation of the empirical data.

@@

<!--Do the main computations for nonparametric analysis of aphid count data-->
```{r stat_aphid_count, echo=F, cache=T, cache.extra=list(seed,data_aphid_count,mtime("good_loclist.R"),mtime("NonParamStat.R"),mtime("vivj_matrix.R"),mtime("CopulaFunctions.R"), mtime("CopulaFunctions_flexible.R"))}

@@

<!--Do the main computations for nonparametric analysis of aphid ff data-->
```{r stat_aphid_ff, echo=F, cache=T,  cache.extra=list(seed,data_aphid_ff,mtime("good_loclist.R"),mtime("NonParamStat.R"),mtime("vivj_matrix.R"),mtime("CopulaFunctions.R"), mtime("CopulaFunctions_flexible.R"))}

@@

<!--
\newpage
## Results: abundance data for *Ceratium furca* in UK seas \label{Ex_pns}
### Model selection approach \label{Ex_pns_Model_selection}
### nonparametric analysis of tail dependence  \label{Ex_pns_NPA}
                          ----moved to Paper.Rmd----
-->

@@

<!--Do the main computations for nonparametric analysis of plankton data-->
```{r stat_plankton_north_sea, echo=F, cache=T, cache=T,  cache.extra=list(seed,data_plankton_north_sea,longs_pns,lats_pns,mtime("good_loclist.R"),mtime("NonParamStat.R"),mtime("vivj_matrix.R"),mtime("CopulaFunctions.R"), mtime("CopulaFunctions_flexible.R"))}

@@

<!--Do the main computations for nonparametric analysis of methane-flux data-->
```{r stat_methane, echo=F, cache=T, cache=T,  cache.extra=list(seed,methane_data,mtime("good_loclist.R"),mtime("NonParamStat.R"),mtime("vivj_matrix.R"),mtime("CopulaFunctions.R"), mtime("CopulaFunctions_flexible.R"))}

@@

\begin{figure}[!h]
\begin{center}
\includegraphics[width=13 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Clayton/common_legend_cause4copula_stat.pdf}\\
\vspace{-0.4 cm}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Clayton/Clayton_Spearman_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Clayton/Clayton_Kendall_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Clayton/Clayton_Pearson_vs_Kendall's Tau.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Clayton/Clayton_Corl_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Clayton/Clayton_Coru_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Clayton/Clayton_Corl-Coru_vs_Kendall's Tau.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Clayton/Clayton_Pl_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Clayton/Clayton_Pu_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Clayton/Clayton_Pl-Pu_vs_Kendall's Tau.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Clayton/Clayton_D2u_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Clayton/Clayton_D2l_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Clayton/Clayton_D2u-D2l_vs_Kendall's Tau.pdf}
\caption[AR(1) model : comparing correlations and nonparametric statistic for between noise-copula (\textbf{Clayton}) and population copula for different Kendall's correlation]{AR(1) model : results of comparison between 3 types of correlation (i.e. Spearman, Kendall, Pearson) and 6 nonparametric stats ($\cor_l$, $\cor_u$, $\Ps_l$, $\Ps_u$, $\Dsq_u$ and $\Dsq_l$) of environmental noise generated from lower tail dependent \textbf{Clayton} copula and of the affected populations for 9 equidistant Kendall's correlation ($\tau$) values in a range (0.1 to 0.9) (Initially $5000$ points are generated but we kept last $500$ points for both noise and population data for comparison). p-values from paired t-test if $> 0.05$ (above horizontal purple line) indicates exactly same estimate between noise and population copulae. \label{fig_Cause4copula_C_kend_ar1}}
\end{center}
\end{figure}

\begin{figure}[!h]
\begin{center}
\includegraphics[width=13 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Survival Clayton/common_legend_cause4copula_stat.pdf}\\
\vspace{-0.4 cm}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Survival Clayton/Survival Clayton_Spearman_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Survival Clayton/Survival Clayton_Kendall_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Survival Clayton/Survival Clayton_Pearson_vs_Kendall's Tau.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Survival Clayton/Survival Clayton_Corl_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Survival Clayton/Survival Clayton_Coru_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Survival Clayton/Survival Clayton_Corl-Coru_vs_Kendall's Tau.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Survival Clayton/Survival Clayton_Pl_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Survival Clayton/Survival Clayton_Pu_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Survival Clayton/Survival Clayton_Pl-Pu_vs_Kendall's Tau.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Survival Clayton/Survival Clayton_D2u_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Survival Clayton/Survival Clayton_D2l_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Survival Clayton/Survival Clayton_D2u-D2l_vs_Kendall's Tau.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Survival Clayton/Survival Clayton_scatter_CorlmCoru_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Survival Clayton/Survival Clayton_scatter_PlmPu_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Survival Clayton/Survival Clayton_scatter_D2umD2l_Kendall's Tau.pdf}
\caption[AR(1) model : comparing correlations and nonparametric statistic between noise-copula (\textbf{Survival Clayton}) and population copula for different Kendall's correlation]{AR(1) model : results of comparison between 3 types of correlation (i.e. Spearman, Kendall, Pearson) and 6 nonparametric stats ($\cor_l$, $\cor_u$, $\Ps_l$, $\Ps_u$, $\Dsq_u$ and $\Dsq_l$) of environmental noise generated from upper tail dependent \textbf{Survival Clayton} copula and of the affected populations for 9 equidistant Kendall's correlation ($\tau$) values in a range (0.1 to 0.9) (Initially $5000$ points are generated but we kept last $500$ points for both noise and population data for comparison). p-values from paired t-test if $> 0.05$ (above horizontal purple line) indicates exactly same estimate between noise and population copulae. Last row in the figure compared the linear regression line with the 1:1 green line and if noise and population tail-dependence stats came up with Pearson correlation p-value $< 0.05$, then they are significantly similar.\label{fig_Cause4copula_SC_kend_ar1}}
\end{center}
\end{figure}

\begin{figure}[!h]
\begin{center}
\includegraphics[width=13 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Gumbel/common_legend_cause4copula_stat.pdf}\\
\vspace{-0.4 cm}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Gumbel/Gumbel_Spearman_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Gumbel/Gumbel_Kendall_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Gumbel/Gumbel_Pearson_vs_Kendall's Tau.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Gumbel/Gumbel_Corl_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Gumbel/Gumbel_Coru_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Gumbel/Gumbel_Corl-Coru_vs_Kendall's Tau.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Gumbel/Gumbel_Pl_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Gumbel/Gumbel_Pu_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Gumbel/Gumbel_Pl-Pu_vs_Kendall's Tau.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Gumbel/Gumbel_D2u_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Gumbel/Gumbel_D2l_vs_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Gumbel/Gumbel_D2u-D2l_vs_Kendall's Tau.pdf}\\
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Gumbel/Gumbel_scatter_CorlmCoru_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Gumbel/Gumbel_scatter_PlmPu_Kendall's Tau.pdf}
\includegraphics[width=5 cm]{./Results/Cause4copula_results/Cause4copula_stat_results_ar1_beta_0.5_Gumbel/Gumbel_scatter_D2umD2l_Kendall's Tau.pdf}
\caption[AR(1) model : comparing correlations and nonparametric statistic between noise-copula (\textbf{Gumbel}) and population copula for different Kendall's correlation]{AR(1) model: similar analysis as depicted in Fig. \ref{fig_Cause4copula_SC_kend_ar1} but for noise generated from upper tail dependent \textbf{Gumbel} copula. \label{fig_Cause4copula_G_kend_ar1}}
\end{center}
\end{figure}
